### 2023-09-07 3.Design/memcell.tex
experimenting with time diagram, not working yet
Now working

>>>>

\begin{figure}[H]
  \centering
  \def\degr{${}^\circ$}
  \begin{tikztimingtable}
    Clock 128\,MHz 0\degr & H 2C N(A1) 8{2C} N(A5) 3{2C} G \\
    Clock 128\,MHz 90\degr & [C] 2{2C} N(A2) 8{2C} N(A6) 2{2C} C \\
    Clock 128\,MHz 180\degr & C 2{2C} N(A3) 8{2C} N(A7) 2{2C} G \\
    Clock 128\,MHz 270\degr & 3{2C} N(A4) 8{2C} N(A8) 2C C \\
    Coarse Pulse & 3L 16H 6L \\
    Coarse Pulse - Delayed 1 & 4L N(B2) 16H N(B6) 5L \\
    Coarse Pulse - Delayed 2 & 5L N(B3) 16H N(B7) 4L \\
    Coarse Pulse - Delayed 3 & 6L 16H 3L \\
    \\
    Final Pulse Set & 3L 16H N(B5) 6L \\
    Final Pulse $\overline{\mbox{Reset}}$ & 6L N(B4) 16H 3L \\
    Final Pulse & 3L N(B1) 19H N(B8) 3L \\
    \extracode
    \tablerules
    \begin{pgfonlayer}{background}
      \foreach \n in {1,...,8}
      \draw [help lines] (A\n) --56(B\n);
    \end{pgfonlayer}
  \end{tikztimingtable}
  \caption{Memory cell symbol with the input pin (left), the output pin (right), the input enable pin (top) and the output enable pin (bottom)}
  \label{fig:memcellCircuit}
\end{figure}
